TE_computation

### 2021-03-22 computational model/TE_computation_Simulation.Rmd
adding spaces between ggplot facets

# Visualizing Simulation 1
Simulation1 <- data_Simulation1 %>%
  # Convert to long data
  pivot_longer(c(W, D, N), names_to = "vocab_type", values_to = "number") %>%
  mutate(vocab_type = factor(vocab_type, levels=c("W", "D", "N"))) %>%
  mutate(vocab_type = recode(vocab_type, 
                             W = "Panel A: Total vocabulary (W)", 
                             D = "Panel B: Dominant vocabulary (D)", 
                             N = "Panel C: Non-dominant vocabulary (N)")) %>%
  mutate(B = as.factor(B)) %>%
  ggplot(aes(x = number, y = TE, color = B)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ vocab_type) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=12)) +
  labs(x = "Number of words", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)"
       #, title = "Number of translation equivalent by balance in relation to different input measures "
       ) +
  guides(colour = guide_legend(nrow = 1))

@@

# Visualizing Simulation 2
Simulation2 <- data_Simulation2 %>%
  mutate(bin_B = case_when(B < 0.6 ~ "0.5",
                           B >= 0.6 & B < 0.7 ~ "0.6",
                           B >= 0.7 & B < 0.8 ~ "0.7",
                           B >= 0.8 & B < 0.9 ~ "0.8",
                           TRUE ~ "0.9")) %>%
  pivot_longer(-c(V, W, B, bin_B), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type %notin% c("D", "N")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("NU", "DU", "TE"))) %>%
  group_by(V, bin_B, vocab_type) %>%
  summarise(n_words = mean(number)) %>%
  ggplot(aes(x = bin_B, y = n_words, fill = vocab_type)) + 
  geom_bar(position="stack", stat="identity") +
  facet_grid(. ~ V) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  #scale_y_continuous(limits = c(0, 1200)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), 
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=12)) + 
  labs(x = "Balance", 
       y = "Number of concepts", 
       title = "Vocabulary composition across different developmental timepoints (V)")

@@

## Visualizing the simulation
Simulation3 <- data_Simulation3 %>%
  ## Calculate where I > 1
  mutate(TE_easier = I1*(D*N/V)) %>%
  ## Calculate where I < 1
  mutate(TE_harder = I2*(D*N/V)) %>%
  # Round to keep whole numbers only
  mutate_at(vars(-B), round, 0) %>%
  # Prepare dataset to plot
  pivot_longer(c(TE, TE_harder, TE_easier), 
               names_to = "Model", values_to = "number_TE") %>%
  mutate(Model = factor(Model, levels=c("TE_harder", "TE", "TE_easier"))) %>%
  mutate(Model = recode(Model, 
                        TE = "I = 1 (assuming independence of D and N)",
                        TE_easier = "I = 1.5 (TEs are more easily learned)",
                        TE_harder = "I = 0.5 (TE are less easily learned)")) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  # ggplot
  ggplot(aes(x = W, y = number_TE, color = bin_B)) +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ Model) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size=12)) +
  labs(x = "Total word vocabulary (W)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))

>>>>

# Visualizing Simulation 1
Simulation1 <- data_Simulation1 %>%
  # Convert to long data
  pivot_longer(c(W, D, N), names_to = "vocab_type", values_to = "number") %>%
  mutate(vocab_type = factor(vocab_type, levels=c("W", "D", "N"))) %>%
  mutate(vocab_type = recode(vocab_type, 
                             W = "Panel A: Total vocabulary (W)", 
                             D = "Panel B: Dominant vocabulary (D)", 
                             N = "Panel C: Non-dominant vocabulary (N)")) %>%
  mutate(B = as.factor(B)) %>%
  ggplot(aes(x = number, y = TE, color = B)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ vocab_type) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=12),
        panel.spacing.x = unit(2, "lines"),
        panel.background = element_rect(fill = NA, color = "black")) +
  labs(x = "Number of words", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)"
       #, title = "Number of translation equivalent by balance in relation to different input measures "
       ) +
  guides(colour = guide_legend(nrow = 1))

@@

# Visualizing Simulation 2
Simulation2 <- data_Simulation2 %>%
  mutate(bin_B = case_when(B < 0.6 ~ "0.5",
                           B >= 0.6 & B < 0.7 ~ "0.6",
                           B >= 0.7 & B < 0.8 ~ "0.7",
                           B >= 0.8 & B < 0.9 ~ "0.8",
                           TRUE ~ "0.9")) %>%
  pivot_longer(-c(V, W, B, bin_B), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type %notin% c("D", "N")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("NU", "DU", "TE"))) %>%
  group_by(V, bin_B, vocab_type) %>%
  summarise(n_words = mean(number)) %>%
  ggplot(aes(x = bin_B, y = n_words, fill = vocab_type)) + 
  geom_bar(position="stack", stat="identity") +
  facet_grid(. ~ V) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), 
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=12),
        panel.spacing.x = unit(2, "lines"),
        panel.background = element_rect(fill = NA, color = "black")) + 
  labs(x = "Balance", 
       y = "Number of concepts", 
       title = "Vocabulary composition across different developmental timepoints (V)")

@@

## Visualizing the simulation
Simulation3 <- data_Simulation3 %>%
  ## Calculate where I > 1
  mutate(TE_easier = I1*(D*N/V)) %>%
  ## Calculate where I < 1
  mutate(TE_harder = I2*(D*N/V)) %>%
  # Round to keep whole numbers only
  mutate_at(vars(-B), round, 0) %>%
  # Prepare dataset to plot
  pivot_longer(c(TE, TE_harder, TE_easier), 
               names_to = "Model", values_to = "number_TE") %>%
  mutate(Model = factor(Model, levels=c("TE_harder", "TE", "TE_easier"))) %>%
  mutate(Model = recode(Model, 
                        TE = "I = 1 (assuming independence of D and N)",
                        TE_easier = "I = 1.5 (TEs are more easily learned)",
                        TE_harder = "I = 0.5 (TE are less easily learned)")) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  # ggplot
  ggplot(aes(x = W, y = number_TE, color = bin_B)) +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ Model) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size=12),
        panel.spacing.x = unit(2, "lines"),
        panel.background = element_rect(fill = NA, color = "black")) +
  labs(x = "Total word vocabulary (W)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))
